Legion: Expressing Locality and Independence with Logical Regions

### 2012-05-05 doc/sc2012/experiments.tex
More small edits

  The regions for the tasks are mapped as 
shown in Figure~\ref{fig:gpumapping}.  Wires and private node data are kept in each GPU's
framebuffer at all times.  An instance of the ``all-shared nodes'' region is placed in
GASNet memory and instances for just the shared and ghost nodes needed by each GPU
are placed into that GPU's zero-copy memory.  This enables the application kernels
to access the data as well as the necessary inter-node exchanges of data via the GASNet
memory.

>>>>

  The regions for the tasks are mapped as 
shown in Figure~\ref{fig:gpumapping}.  Wires and private node data are kept in each GPU's
framebuffer at all times.  An instance of the all-shared-nodes region is placed in
GASNet memory and instances for just the shared and ghost nodes needed by each GPU
are placed into that GPU's zero-copy memory.  This enables the application kernels
to access the data as well as the necessary inter-node exchanges of data via the GASNet
memory.
